Supplemental Information: Continuous developmental changes in word recognition support language learning across early childhood

### 2025-04-04 paper/supplemental_information.Rmd
fix flipped axis labels

```{r dataset, fig.cap="\\label{fig:dataset} Age distribution for each dataset, using three-month bins.", fig.pos="h!"}
ggplot(d_sub, aes(x = age))+ 
  geom_histogram(binwidth = 3) + 
  facet_wrap(~dataset_name, scale = "free_y") +
  xlab("Number of participants") + 
  ylab("Age (months)")
```

>>>>

```{r dataset, fig.cap="\\label{fig:dataset} Age distribution for each dataset, using three-month bins.", fig.pos="h!"}
ggplot(d_sub, aes(x = age))+ 
  geom_histogram(binwidth = 3) + 
  facet_wrap(~dataset_name, scale = "free_y") +
  xlab("Age (months)") + 
  ylab("Number of participants")
```
